---
title: "Figures"
author: "Jill Deines"
date: "8/24/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---

Goal: Make study area figure

Items to plot:

* groundwater depletion timeframes
* current irrigation
* county bounds

```{r knitrOpts, echo=FALSE}
library(knitr)
opts_chunk$set(cache=FALSE, fig.path='../figure/02.10_figStudyArea/')
```

**R Packages Needed**

```{r packages, message=FALSE, echo=TRUE, eval=TRUE}
library(tidyverse)
library(sf)
library(here)  
library(raster)

library(rgdal)
library(latticeExtra)
library(RColorBrewer)

# directories:
rootDir <- here::here() # for setting path to local repo data folder

sessionInfo()
```


# Load

## Spatial Boundaries
Reproject to the MSU CLASS project projection, which is an AEA with a modified center line so the aquifer is centered and aligned vertically

```{r loadSpatial}
# load county polygons
gisDir <- paste0(rootDir, '/data/gis/boundaries')
classProj <- '+proj=aea +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-101 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0'

counties <- read_sf(paste0(gisDir,
        '/tigris_2012_counties_100_inMinBoundBuff.geojson')) %>%
  st_transform(classProj) %>%
  rename(fips5 = masterid) %>%
  dplyr::select(c(fips5))

# background polygons as spdf
states_sf <- read_sf(paste0(gisDir, '/States_continental.shp')) %>%
  st_transform(classProj) 
states <- states_sf %>%
  as_Spatial()

minBound <- read_sf(paste0(gisDir,'/HPA_MinimumBound.shp')) %>%
  st_transform(classProj) %>%
  as_Spatial()

aquifer_sf <- read_sf(paste0(gisDir,'/Aquifer_Regions_dissolve.shp')) %>%
  st_transform(classProj) %>%
  st_simplify()
aquifer <- aquifer_sf %>%
  as_Spatial()

county6 <- counties %>% 
  filter(fips5 %in% c('20055','48111','31057','08125','35041','40139')) %>%
  as_Spatial()
```

# Make maps

## Depletion

laod depletion data

```{r loaddepletion}
rasDir <- paste0(rootDir, '/data/gis/studyArea_rasters')

depletion <- raster(paste0(rasDir, '/depletion_predictions_Haacker2016.tif'))

# reproject and clip precip
depletionClass <- projectRaster(depletion, res = 1000, crs=classProj)
depletionClassCrop <- crop(depletionClass, aquifer)
depletionClassMask <- mask(depletionClassCrop, aquifer)
# set max visuzalized values between 2300-2400 class
depletionClassMask[depletionClassMask > 2390] <- 2350
```

```{r depletionMap, fig.width = 3, fig.height = 5, dev = 'png',  dpi = 300}
palNum <- 9
breaks <- c(2000,2025,2050,2075,2100,2125,2150,2175,2200,2300,3500)

colPal <- rev(brewer.pal(palNum, 'YlOrRd'))

depPal2 <- c(colPal,'gray60')

# no lines
spplot(depletionClassMask, col.regions = depPal2,  colorkey=list(space='bottom'),
       at = c(2000,2025,2050,2075,2100,2125,2150,2175,2200,2300,2400),
       axes = TRUE,
       maxpixels = 1000000,
       par.settings=list(axis.line=list(col=NA))) +
  latticeExtra::layer(sp.polygons(aquifer, fill = 'gray10',lwd=.8),under=T) +
  latticeExtra::layer(sp.polygons(aquifer, lwd=.8))  +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col='gray20')) +
  latticeExtra::layer(sp.polygons(county6, lwd = 2, col = 'blue'))

# for color key with outlines
spplot(depletionClassMask, col.regions = depPal2,  colorkey=list(space='bottom'),
       at = c(2000,2025,2050,2075,2100,2125,2150,2175,2200,2300,2400),
       axes = TRUE) +
  latticeExtra::layer(sp.polygons(aquifer, fill = 'gray10',lwd=.8),under=T)   +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col='gray30')) 
```

## Irrigation: Current

load irrigated area

```{r irrLoad}
irrigation <- raster(paste0(rasDir,
               '/2015-2017_AIM-HPA_finalMaps_currentIrrigation.tif'))

irrClass <- projectRaster(irrigation, res = 450, crs=classProj)
irrClassCrop <- crop(irrClass, aquifer)
irrClassMask <- mask(irrClassCrop, aquifer)
```


```{r irrMap, fig.width = 3, fig.height = 5, dev = 'png', dpi = 300}

# no lines
spplot(irrClassMask, col.regions = c('gray50','darkgoldenrod1'), 
       at = c(0,.9,1.1),
       colorkey=list(space='bottom'),
       maxpixels = 1000000,
       par.settings=list(axis.line=list(col=NA))) +
  #latticeExtra::layer(sp.polygons(aquifer, fill = 'gray10',lwd=.8),under=T) +
  latticeExtra::layer(sp.polygons(aquifer, lwd=.8))  +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col='gray20')) +
  latticeExtra::layer(sp.polygons(county6, lwd = 2, col = 'blue'))
```

# inset

```{r inset, fig.width = 2, fig.height = 1.5, dpi = 300, dev = c('png','pdf')}
plot(states_sf[1], col = NA, reset = FALSE, main = NA)
#plot(minBound_sf, col = 'lightblue', add = TRUE, border = 'lightblue')
plot(aquifer_sf, col = 'dodgerblue1', add = TRUE, lwd = 0.25, border = 'gray35')
plot(states_sf[1], col = NA, add = TRUE)
```

