---
title: "Figure 2: Irrigation Projections by County"
author: "Jill Deines"
date: "8/17/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---

Goal: Make figure showing results by county

Items to plot:

* total irrigated acres lost by 2100
* percent of lost acres going to pasture

```{r knitrOpts, echo=FALSE}
library(knitr)
opts_chunk$set(cache=FALSE, fig.path='../figure/02.20_figsCountyProjections/')
```

**R Packages Needed**

```{r packages, message=FALSE, echo=TRUE, eval=TRUE}
library(tidyverse)
library(sf)
library(here)  

library(rgdal)
library(latticeExtra)
library(RColorBrewer)

# directories:
rootDir <- here::here() # for setting path to local repo data folder

# formatted data master file (in data/tabular)
masterFilename <- 'counties_allAquiferContained_Irr_currentRecent_rserev1_annualIrrLoss_rsSuit_acres_billFormated_allCounties_master.csv'

sessionInfo()
```


# Load

## Spatial Boundaries
Reproject to the MSU CLASS project projection, which is an AEA with a modified center line so the aquifer is centered and aligned vertically

```{r loadSpatial}
# load county polygons
gisDir <- paste0(rootDir, '/data/gis/boundaries')
classProj <- '+proj=aea +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-101 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0'

counties <- read_sf(paste0(gisDir,
        '/tigris_2012_counties_100_inMinBoundBuff.geojson')) %>%
  st_transform(classProj) %>%
  rename(fips5 = masterid) %>%
  dplyr::select(c(fips5))

county6 <- counties %>% 
  filter(fips5 %in% c('20055','48111','31057','08125','35041','40139')) %>%
  as_Spatial()

# bakcground polygons as spdf
states <- read_sf(paste0(gisDir, '/States_continental.shp')) %>%
  st_transform(classProj) %>%
  as_Spatial()

minBound <- read_sf(paste0(gisDir,'/HPA_MinimumBound.shp')) %>%
  st_transform(classProj) %>%
  as_Spatial()

aquifer <- read_sf(paste0(gisDir,'/Aquifer_Regions_dissolve.shp')) %>%
  st_transform(classProj) %>%
  st_simplify() %>%
  as_Spatial()
```

## Datasets
this was in acres for bill, so convert to ha

```{r loadData}
master0 <- read_csv(paste0(rootDir, '/data/tabular/', masterFilename))

# extract values of interest
master <- master0 %>%
  filter(year == 2100) %>%
  mutate(irrAreaLost_ha = (totalLostDrylandAg + totalLostPasture) /  2.471,
           percentLost_pasture = percentLost_pasture*100,
         percentLost_pasture2 = (totalLostPasture/(totalLostDrylandAg + totalLostPasture) )*100) %>%
  dplyr::select(fips5, currentIrr_20152017_acres, active, irrAreaLost_ha, totalLostDrylandAg, totalLostPasture, percentLost_pasture, percentLost_pasture2)

# spatialize county numbers and fix county sf object for spdf conversion
countyData <- counties %>%
  left_join(master, by = 'fips5') %>%
  mutate(irrAreaLost_1000ha = irrAreaLost_ha / 1000)

# set NA values to 0
countyData[is.na(countyData$irrAreaLost_1000ha),'irrAreaLost_1000ha'] <- 0
countyData[is.na(countyData$percentLost_pasture),'percentLost_pasture'] <- 0


types <- vapply(st_geometry(countyData), function(x) {
  class(x)[2]
}, '')
countyData2 <- countyData[grepl('*POLYGON', types),]

bad <-  countyData[!grepl('*POLYGON', types),]
test <- st_collection_extract(bad, "POLYGON")

countyData3 <- rbind(countyData2, test)

countySp <- as(countyData3, 'Spatial')


```


# Make maps

## vis parameters

```{r mapVisParams}
panelBackground <- 'gray5'
stateLines <- 'gray10'
stateFill <- 'gray80'
aquiferFill <- 'gray20'
aimFill <- 'gray50'
mapXLim <- c(-430000,440000)
mapYLim <- c(-1000000,450000)

irrLossPalette <- brewer.pal(n = 9, name = 'OrRd')
irrLossRamp <- colorRampPalette(irrLossPalette)

pasturePal2 <- brewer.pal(n=9, name = 'YlGnBu')
pasturePal2Ramp <- colorRampPalette(pasturePal2)

pasturePal3 <- brewer.pal(n=9, name = 'GnBu')
pasturePal3Ramp <- colorRampPalette(pasturePal3)
```

## Irrigated Area Loss by County (2100)

```{r countyIrrLoss2100, fig.width = 3, fig.height = 5, dev = c('png','pdf'), dpi = 300}

spplot(countySp, 'irrAreaLost_1000ha', col.regions = c('gray50',irrLossRamp(19)),
       xlim = mapXLim, ylim = mapYLim,
       colorkey = list(space = 'bottom'),
       par.settings = list(panel.background = list(col=panelBackground))) +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col=stateLines)) +
  latticeExtra::layer(sp.polygons(aquifer, lwd=.8, col=NA, fill = aquiferFill), under=T) +
   # latticeExtra::layer(sp.polygons(minBound, lwd=.8, col=NA, fill = aimFill), under=T) +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col=NA, fill = stateFill), under = TRUE) +
  latticeExtra::layer(sp.polygons(county6, lwd = 2, col = 'blue'))
```

## Proportion Pasture


```{r pasturePercentLoss2100_percentOfStart_color2, fig.width = 3, fig.height = 5, dev = c('png','pdf'), dpi = 300}

spplot(countySp, 'percentLost_pasture', 
       col.regions = c('gray50',pasturePal2Ramp(19)),
       xlim = mapXLim, ylim = mapYLim,
       colorkey = list(space = 'bottom'),
       par.settings = list(panel.background = list(col=panelBackground))) +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col=stateLines)) +
  latticeExtra::layer(sp.polygons(aquifer, lwd=.8, col=NA, fill = aquiferFill), under=T) +
   # latticeExtra::layer(sp.polygons(minBound, lwd=.8, col=NA, fill = aimFill), under=T) +
  latticeExtra::layer(sp.polygons(states, lwd=.8, col=NA, fill = stateFill), under = TRUE)  +
  latticeExtra::layer(sp.polygons(county6, lwd = 1.75, col = 'darkorchid2'))
```

